Syntactic realization with data-driven neural tree grammars

### 2016-10-10 paper/draft.tex
adding more numbers, appendix

@@

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} & \textbf{After A*}  \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\% \\ \cline{2-4}
         &  Token       &  60.69\% & 55.56\% \\ \cline{2-4}
         & Minimal Token & 52.09\% & 54.18\% \\ \cline{2-4}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% \\ \cline{2-4}
         &  Token       &  82.65\% & 62.73\% \\ \cline{2-4}
         &  Minimal Token & 10.13\% & 19.66\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:accresults}
\caption{Classification accuracy by supertag and its individual properties}
\end{figure}

@@

\appendix

>>>>

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}}&\multicolumn{1}{}{} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} 
& \textbf{After A*} & Running Time \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\%  & 1.97s \\ \cline{2-5}
         &  Token       &  60.69\% & 55.56\% & 1.81s \\ \cline{2-5}
         & Minimal Token & 52.09\% & 54.18\% & 2.02s \\ \cline{2-5}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% & 0.30s \\ \cline{2-5}
         &  Token       &  82.65\% & 62.73\% & 0.36s\\ \cline{2-5}
         &  Minimal Token & 10.13\% & 19.66\% & 0.54 \\ \cline{2-5}
\hline
\end{tabular}
\label{table:accresults}
\caption{For each supertag and embedding pair, the mean accuracy of supertag classification before and after the A* algorithm is shown. Also shown is the median running time---which includes model computation and A* search.}
\end{figure}

@@

@@

\newpage
\appendix

\section{Appendix}

\begin{figure}
\centering
\begin{tabular}{|p{6cm}|r|}
\hline
Model Parameter & Value \\ \hline
Convolution filter size & 48 \\ \hline
Optimization Algorithm & ADAM \\ \hline
Learning Rate & 0.0001 \\ \hline
Dense-Layer Dropout Rates & 0.5 \\ \hline
\end{tabular}
\label{table:params}
\caption{.}
\end{figure}

\subsection{Data}

This work used data processed from the Wall Street Journal portion of the Treebank corpus. Specifically, section 02-21 were used for training, section 22 for development, and section 23 for testing.  The corpus was preprocessed using the Stanford Parser to fix some common issues as well as remove information extra to syntactic category.  The resulting parse trees were processed.  They were annotated with head rules that marked the head at each node in the parse tree and which nodes were dependents or adjuncts.  These annotated trees were split at adjunction and substitution positions to form the grammar.  For the dependency structures used in the models, we use the derivation tree formed by the grammar for each parse tree.  The derivation structures were further processed to parent-child pairs and top-down traversals for each of the models.  The preprocessing and processing code are distributed with this paper.

\subsection{Model parameters}

For the convolutional embeddings, we used
